### 2019-07-12 manuscript/results.tex
minor editing to the resuls (referrences fixed)

\subsection{Models}
\subsubsection{Ploidy and diversification}
When considering ploidy alone (M1. $D/P$ model), we found a greater net diversification rate for diploids than for polyploids, in agreement with \citet{mayrose_2011, mayrose_2015}.
This result holds with (\cref{figure:netdivall}A) or without ( M6 \cref{suppfigure:alldip}A) the diploidization parameter.
Incorporating a hidden state in this model, however, reduces the clear separation in diversification rate estimates between diploids and polyploids (M4. $D/P+A/B$ asym model; \cref{figure:netdivall}B, and M9 \cref{figure:alldip}B).
Thus, differences in net diversification rates are explained by an unknown factor as well as by ploidy.
This specific result is also supported by the Bayes factors shown in table \cref{table:bayesfactors} where both model M4 and the character independent model M2 have equal evidence of  being preferred over every other model of ploidy. See table \cref{supptable:M6M7} showing analogous results when diploidzation is accounted for.

\subsubsection{Breeding system and diversification}
When considering breeding system alone (M11. $I/C$ model, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}.
When a hidden state is included (M14. $I/C+A/B$ model), the large net diversification rate difference persists for hidden state $A$ but and it slightly overlaps in the  hidden state $B$ (\cref{figure:netdivall}D).
When calculating Bayes factors for all breeding system models (M11-M15) we found that the best two supported models are the models with hidden states and asymmetric transition rates (M14 and M15 \cref{table:M11M15})
Thus, differences in net diversification rates are best explained by both breeding system and an unknown factor \citep[as in Onagraceae;][]{freyman_2019} and not only by the focal trait nor an unknown factor.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.

\subsubsection{Ploidy, breeding system, and diversification}
When considering ploidy and breeding system together (M16. $ID/CD/CP$ model), the net diversification rate for SI diploids was greater than for either SC diploids or SC polyploids, with or without diploidization (M16 \cref{figure:netdivall}E, M21\cref{suppfigure:dipall}E).
Thus, the difference in net diversification associated with breeding system persists even when ploidy is included in the model.
The reverse is not true, though: the association of ploidy with net diversification in the M1. $D/P$ model (\cref{figure:netdivall}A, \cref{suppfigure:dipall}A) appears to be driven by the subset of diploids that are SI; among SC species, net diversification rates for diploids and polyploids not as distinct.
%
When a hidden state is included (M19. $IC/CD/CP+A/B$ model) the net diversification rate separation amongst states ID and (CD, CP)  is clear under hidden state A, but under hidden state B the separation exist between states ID and CP while CD overlaps with the former two (\cref{figure:netdivall}F).
The same general pattern remains when diploidization is included (\cref{suppfigure:alldip}F), but the hidden states are reversed.
Bayes factors for the three state models that include the character independent model show very strong support preferring asymmetric hidden state with the focal traits models shown in table \cref{supptable:M16M20} (with diploidization \cref{supptable:M21M25}).

\subsubsection{Lumped models}
When comparing model M26. Lumped $D/P$ against M16. $ID/CD/CP$ (\cref{figure:lumped}B and C) Bayes factors reveal moderate support ($K=4.1$) preferring the three state model instead of the two state model(\cref{table:lumped}).
A similar result was obtained when comparing the lumped model for ploidy but in the presence of hidden states (model M27 \textit{vs.} M23 \cref{table:lumped},\cref{suppfigure:lumpedDP}E and F).

We also compared lumped models for breeding system to test for the inclusion of ploidy state (M28\cref{figure:lumped}E \textit{vs.} M16\cref{figure:lumped}C) and we found no evidence preferring the three-state over the two state-model ($K=-0.6$, \cref{table:lumped}).
However, when accounting for hidden state,  the three-state model MM18. $I/C/CD/CP+A/B$ (\cref{suppigure:lumpedIC}F) was moderately preferred ($K=2.6$)over the lumped model M29.(\cref{suppfigure:lumpedIC}E).

@@

\subsection{Model selection key questions}
\subsubsection{Are diversification patterns only determined by hidden states?}
Whether the determination of the diversification is dependent on the focal traits and not a hidden state only was done via the comparisons of character independent models against the focal traits  models, or against the focal traits with hidden states (results shown in tables \cref{table: bayesfactors},\cref{table:M11M15},\cref{supptable:M6M10},\cref{supptable:M16M20},\cref{supptable:M21M25}).
The general pattern is to moderately to strongly prefer models with focal traits and asymetric hidden states over the rest of the models with the exception of the ploidy only model where the character independent model (M2) seems to be equally preferred($K=0.5$) as the model with ploidy and asymmetric hidden rates (M4, \cref{table:revbayes}).

@@

\subsubsection{Is a second trait adding information to the diversification process?}
As summarized in table \cref{table:lumped} it is moderately preferred to add breeding system to ploidy only models (cref{figure:lumpedDP}).
When adding ploidy information to breeding system models to create a three-state model, we found that there is no evidence that it is preferred (M28 vs. M16 \cref{figure:lumpedIC}B and C). 
However, it becomes moderately preferable in the presence of hidden states (M29 vs. M23  \cref{figure:lumpedIC}E and C)

\subsubsection{Is there evidence for diploidization?}
We considered models both with and without diploidization in order to explore its effects on the estimates of state-dependent diversification.
For the models that only include diploid and polyploid states (M6-M10) the results are similar in terms of the effect of diversification (\cref{figure:dipall}).
When comparing models with diploidization against models without diploidization we found moderate evidence that models containing the parameter $\delta$ are preferred over models without diploidization (summarized in table \cref{supptable:testdiploidization})

\subsubsection{Do asymmetric rates in hidden states models affect the pattern of diversification?}
When comparing different types of asymmetry across hidden states models we found that the asymmetry did not change the direction of effects in net diversification results as shown in \cref{suppfigure:asymmetric}. However, models with asymmetric hidden rates are strongly preferred over models with equal rates between hidden states (summarized in \cref{supptable:asymmetry}).

@@

\begin{supptable}
\addtolength{\tabcolsep}{-5pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                                    & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=log(BF(M1,M2) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M1. D/P                                  & -1238.76                                                          & M1 vs. M4   & 60.47           & M4 (Strong)                                                          \\
\textbf{M4. D/P+A/B asym}                & \textbf{-1223.28}                                                &             &                 &                                                                      \\ \hline
M11. I/C                                 & -1309.07                                                          & M11 vs. M14 & 61.35           & M14 (Strong)                                                         \\
\textbf{M14. I/C+A/B asym}               & \textbf{-1247.72}                                                 &             &                 &                                                                      \\ \hline
M16. ID/CD/CP                            & -1459.11                                                          & M16 vs. M19 & 65.90           & M19 (Strong)                                                         \\
\textbf{M19. ID/CD/CP+A/B asym}          & \textbf{-1393.20}                                                &             &                 &                                                                      \\ \hline
M6. D/P+$\delta$                         & -1283.76                                                          & M6 vs. M9   & 69.3            & M9 (Strong)                                                          \\
\textbf{M9. D/P+A/B+$\delta$ asym}       & \textbf{-1214.46}                                                 &             &                 &                                                                      \\ \hline
M21. IC/CD/CP+$\delta$                   & -1454.68                                                          & M21 vs. M24 & 68.48           & M24 (Strong)                                                         \\
\textbf{M24. IC/CD/CP+A/B+$\delta$ asym} & \textbf{-1386.20}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Test for addition of hidden states in models via Bayes factors. Models with hidden states are strongly preferred over simpler models}
\label{table:testaddhidden}
\end{supptable}

>>>>

\subsection{Models}
\subsubsection{Ploidy and diversification}
When considering ploidy alone (M1. $D/P$ model), we found a larger net diversification rate for diploids than for polyploids, in agreement with \citet{mayrose_2011, mayrose_2015}.
This result holds with (\cref{figure:netdivall}A) or with the diploidization parameter (model M6 \cref{suppfigure:alldip}A) .
Incorporating a hidden state in this model, however, reduces the clear separation in diversification rate estimates between diploids and polyploids (M4. $D/P+A/B$ asym model; \cref{figure:netdivall}B, and M9 \cref{suppfigure:alldip}B).
Thus, differences in net diversification rates are explained by an unknown factor.
The lack of differences between diploid and polyploid net diversification rates is also supported by the Bayes factors shown in table \cref{table:bayesfactors} where both model M4 and the character independent model M2 have equal evidence of  being preferred over every other model of ploidy. See table \cref{supptable:M6M10} showing analogous results when diploidzation is accounted for.

\subsubsection{Breeding system and diversification}
When considering breeding system alone (M11. $I/C$ model, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}.
When a hidden state is included (M14. $I/C+A/B$ model), the large net diversification rate difference persists for hidden state $A$ but and it slightly overlaps in the  hidden state $B$ (\cref{figure:netdivall}D).
When calculating Bayes factors for all breeding system models (M11-M15) we found that the best two supported models are the models with at least asymmetric hidden states (M14 and M15 \cref{table:M11M15})
Thus, differences in net diversification rates are best explained by both breeding system and an unknown factor \citep[as in Onagraceae;][]{freyman_2019} and not only by the focal trait nor an unknown factor.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.

\subsubsection{Ploidy, breeding system, and diversification}
When considering ploidy and breeding system together (M16. $ID/CD/CP$ model), the net diversification rate for SI diploids was greater than for either SC diploids or SC polyploids, with or without diploidization (M16 \cref{figure:netdivall}E, M21\cref{suppfigure:alldip}E).
Thus, the difference in net diversification associated with breeding system persists even when ploidy is included in the model.
The reverse is not true, the association of ploidy with net diversification in the M1. $D/P$ model (\cref{figure:netdivall}A, \cref{suppfigure:alldip}A) appears to be driven by the subset of diploids that are SI; among SC species, net diversification rates for diploids and polyploids is not distinct.

When a hidden state is included (M19. $IC/CD/CP+A/B$ model) the net diversification rate separation amongst states ID and (CD, CP)  is clear under hidden state A, but under hidden state B the separation exist between states ID and CP, while CD overlaps with the other two states (\cref{figure:netdivall}F).
The same general pattern remains when diploidization is included (\cref{suppfigure:alldip}F), but the hidden states are reversed in the x-axis.
Bayes factors for the three state models that include the character independent model show very strong support preferring asymmetric hidden state with the focal traits models shown in  \cref{supptable:M16M20} (with diploidization \cref{supptable:M21M25}).

\subsubsection{Lumped models}
When comparing model M26. Lumped $D/P$ against M16. $ID/CD/CP$ (\cref{figure:lumped}B and C) Bayes factors reveal moderate support ($K=4.1$) preferring the three state model instead of the two state model (\cref{table:lumped}).
A similar result was obtained when comparing the lumped model for ploidy but in the presence of hidden states (model M27 \textit{vs.} M23 \cref{table:lumped}, \cref{suppfigure:lumpedDP}E and F).

We also compared lumped models for breeding system to test for the inclusion of ploidy state (M28 \cref{figure:lumped}E \textit{vs.} M16 \cref{figure:lumped}C) and we found no evidence preferring the three-state over the two state-model ($K=-0.6$, \cref{table:lumped}).
However, when accounting for hidden state,  the three-state model M18. $I/C/CD/CP+A/B$ (\cref{suppfigure:lumpedIC}F) was moderately preferred ($K=2.6$) over the lumped model M29.(\cref{suppfigure:lumpedIC}E).

@@

\subsection{Model selection key questions}
\subsubsection{Are diversification patterns only determined by hidden states?}
Whether the determination of the diversification is dependent on the focal traits and not only on the hidden state was done via the comparisons of character independent models against the focal traits w/o hidden states models (results shown in  \cref{table:bayesfactors},\cref{table:M11M15},\cref{supptable:M6M10},\cref{supptable:M16M20},\cref{supptable:M21M25}).
The general pattern is to moderate- to strongly prefer models with focal traits and asymmetric hidden states over the rest of the models with the exception of the ploidy only model where the character independent model (M2) seems to be equally preferred($K=0.5$) as the model with ploidy and asymmetric hidden rates (M4, \cref{table:bayesfactors}).

@@

\subsubsection{Is a second trait adding information to the diversification process?}
As summarized in  \cref{table:lumped}, it is moderately preferred to add breeding system to ploidy only models (\cref{suppfigure:lumpedDP}).
When adding ploidy information to breeding system models to create a three-state model, we found that there is no evidence that it is preferred (M28 vs. M16 \cref{suppfigure:lumpedIC}B and C). 
However, it becomes moderately preferable in the presence of hidden states (M29 vs. M23  \cref{suppfigure:lumpedIC}E and C).

\subsubsection{Is there evidence for diploidization?}
We considered models both with and without diploidization in order to explore its effects on the estimates of state-dependent diversification.
For the models that only include diploid and polyploid states (M6-M10) the results are similar in terms of the effect of diversification (\cref{figure:alldip}).
When comparing models with diploidization against models without diploidization we found moderate evidence that models containing the parameter $\delta$ are preferred over models without diploidization (summarized in \cref{supptable:testdiploidization}).

\subsubsection{Do asymmetric rates in hidden states models affect the pattern of diversification?}
When comparing different types of asymmetry across hidden states models we found that the asymmetry did not change the direction of effects in net diversification results . However, models with asymmetric hidden rates reduced the overlap amongst net diversification posterior distributions as shown in \cref{suppfigure:asymmetric}. Furthermore, hidden state models with asymmetric traits are strongly preferred over models with equal rates between hidden states (summarized in \cref{supptable:asymmetry}).

@@

\begin{supptable}
\addtolength{\tabcolsep}{-5pt}
\begin{tabular}{|l|c|c|c|c|}
\hline
Model                                    & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & Comparison  & K=log(BF(M1,M2) & \begin{tabular}[c]{@{}l@{}}Preferred\\ Model (Evidence)\end{tabular} \\ \hline
M1. D/P                                  & -1238.76                                                          & M1 vs. M4   & 60.47           & M4 (Strong)                                                          \\
\textbf{M4. D/P+A/B asym}                & \textbf{-1223.28}                                                &             &                 &                                                                      \\ \hline
M11. I/C                                 & -1309.07                                                          & M11 vs. M14 & 61.35           & M14 (Strong)                                                         \\
\textbf{M14. I/C+A/B asym}               & \textbf{-1247.72}                                                 &             &                 &                                                                      \\ \hline
M16. ID/CD/CP                            & -1459.11                                                          & M16 vs. M19 & 65.90           & M19 (Strong)                                                         \\
\textbf{M19. ID/CD/CP+A/B asym}          & \textbf{-1393.20}                                                &             &                 &                                                                      \\ \hline
M6. D/P+$\delta$                         & -1283.76                                                          & M6 vs. M9   & 69.3            & M9 (Strong)                                                          \\
\textbf{M9. D/P+A/B+$\delta$ asym}       & \textbf{-1214.46}                                                 &             &                 &                                                                      \\ \hline
M21. IC/CD/CP+$\delta$                   & -1454.68                                                          & M21 vs. M24 & 68.48           & M24 (Strong)                                                         \\
\textbf{M24. IC/CD/CP+A/B+$\delta$ asym} & \textbf{-1386.20}                                                 &             &                 &                                                                      \\ \hline
\end{tabular}
\caption{Test for addition of hidden states in models via Bayes factors. Models with hidden states are strongly preferred over simpler models}
\label{supptable:testaddhidden}
\end{supptable}
